Case Study (McKenna)

### 2020-06-03 Code/mrp/Case Study (McKenna) .Rmd
Downes logit model runs

```{r}
# Observations. 
downes_list <- list(
  outcome = sample$service_failure,
  male = sample$male,
  age = sample$age, 
  eth = sample$eth, 
  income = sample$income,
  state = sample$state,
  n = length(sample$service_failure), 
  n_male = max(sample$male),
  n_age = max(sample$age),
  n_eth = max(sample$eth),
  n_income = max(sample$income),
  n_state = max(sample$state)
)

# Define parameters for Hamiltonian Monte Carlo algorithm
n_iter <- 1000
n_chain <- 4
n_sim <- (n_iter * n_chain)/2

```

```{r, eval = FALSE}
stanfit_final <- stan(file = "downes_copy.stan",
                        data = downes_list, 
                        iter = n_iter, chains = 1)
```
#### Stan user guide logit model 
```{r}
stan_data <- list( 
  age = sample$age, 
  eth = sample$eth, 
  income = sample$income, 
  male = sample$male, 
  state = sample$state, 
  Y = sample$service_failure, 
  N = length(sample$service_failure)
  )
```

>>>>

```{r}
# Observations. 
downes_list <- list(
  outcome = sample$service_failure,
  male = sample$male + 1,
  age = sample$age, 
  eth = sample$eth, 
  income = sample$income,
  state = sample$state,
  n = length(sample$service_failure), 
  n_male = max(sample$male) + 1,
  n_age = max(sample$age),
  n_eth = max(sample$eth),
  n_income = max(sample$income),
  n_state = max(sample$state)
)
```

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "downes_copy.stan"),
  data = downes_list,
  seed = 42 
)
```

#### Stan user guide logit model

```{r}
stan_data <- list( 
  age = sample$age, 
  eth = sample$eth, 
  income = sample$income, 
  male = sample$male, 
  state = sample$state, 
  Y = sample$service_failure, 
  N = length(sample$service_failure)
  )
```
